Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation with Real-Time Maude

### 2015-11-05 RMS/submission.tex
finished the figure of counterexample

\usepackage{alltt}
\usepackage{epic}
\usepackage{pstricks}
\usepackage{tikz}
\newcommand{\hide}[1]{\ignorespaces}
\newcommand{\jx}[1]{{\bf Jiaxiang: }#1{ \bf End}}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}

@@

\begin{figure*}[!t]
\centering
\begin{picture}(300,120)(0,-10)
\thicklines
\put(0,0){\vector(1,0){320}}
\put(305,5){time(${\mu}s$)}
\thinlines
\put(0,0){\line(0,1){110}}
\put(-25,97){task$0$}
\put(-25,77){task$1$}
\put(-25,57){task$2$}
\put(-50,37){scheduling}
\put(-45,17){switching}
\put(-2,-8){$0$}

@@

\end{picture}
\caption{An Counterexample of Scenario (iv).}
\label{f:counterexample}
\end{figure*}

\begin{figure*}[!t]
\centering
\begin{tikzpicture}[
    % styles
    system task/.style={fill=gray!70,draw=gray},
    periodic task/.style={fill=gray!70!black,draw=gray!50!black},
    task line/.style={gray!30,very thin},
    time line/.style={gray!50,very thin,dashed}]

  \foreach \x in {0.5,1.2,...,3.3}
    \draw[task line] (0,\x) -- (15.7,\x);
  \draw[->,thick] (0,0) -- (16,0);
  \draw[thin] (0,0) -- (0,3.8);

  \draw[time line] (0.5,3.3) -- (0.5,0);
  \draw[time line] (2.5,3.3) -- (2.5,0);
  \filldraw[system task] (0,1.2) rectangle +(0.5,0.2);
  \filldraw[periodic task] (0.5,3.3) rectangle +(2,0.2);
  \filldraw[system task] (2.5,0.5) rectangle +(0.25,0.2);
  \filldraw[periodic task] (2.75,2.6) rectangle +(1.25,0.2);
  \filldraw[system task] (4,0.5) rectangle +(0.25,0.2);
  \filldraw[periodic task] (4.25,1.9) rectangle +(0.75,0.2);

@@

  \filldraw[system task] (10,1.2) rectangle +(0.5,0.2);
  \filldraw[periodic task] (10.5,3.3) rectangle +(2,0.2);
  \filldraw[system task] (12.5,0.5) rectangle +(0.25,0.2);
  \filldraw[periodic task] (12.75,2.6) rectangle +(1.25,0.2);
  \filldraw[system task] (14,0.5) rectangle +(0.25,0.2);
  \filldraw[periodic task] (14.25,1.9) rectangle +(0.75,0.2);
\end{tikzpicture}
\caption{An Counterexample of Scenario (iv).}
\label{f:tikz}
\end{figure*}

>>>>

\usepackage{alltt}
%\usepackage{epic}
%\usepackage{pstricks}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\newcommand{\hide}[1]{\ignorespaces}
\newcommand{\jx}[1]{{\bf Jiaxiang: }#1{ \bf End}}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}

@@

\hide{
\begin{figure*}[!t]
\centering
\begin{picture}(300,120)(0,-10)
\thicklines
\put(0,0){\vector(1,0){320}}
\put(305,5){time(${\mu}s$)}
\thinlines
\put(0,0){\line(0,1){110}}
\put(-25,97){task$0$}
\put(-25,77){task$1$}
\put(-25,57){task$2$}
\put(-50,37){scheduling}
\put(-45,17){switching}
\put(-2,-8){$0$}

@@

\end{picture}
\caption{An Counterexample of Scenario (iv).}
\label{f:counterexample}
\end{figure*}
}

\begin{figure*}[!t]
\centering
\begin{tikzpicture}[font=\small,
    % styles
    system task/.style={fill=gray!70,draw=gray},
    periodic task/.style={fill=gray!70!black,draw=gray!50!black},
    task line/.style={gray!30,very thin},
    time line/.style={gray!50,very thin,dashed},
    short line/.style={gray!50,very thin,dashed},
    init/.style={{Triangle[fill=white,scale=1.3]}-},
    complete/.style={{Triangle[scale=1.3]}-}]

  % grid
  \foreach \x in {0.5,1.2,...,3.3}
    \draw[task line] (0,\x) -- (15.7,\x);

  % time indicator
  \draw (0,0) node [below] {$0$};
  \draw[time line] (0.5,3.3) -- (0.5,0);
  \draw (0.5,-0.35) node [below] {$38$} [short line] -- +(0,0.35);
  \draw (0.5,-3pt) -- (0.5,3pt);
  \draw[time line] (2.5,3.3) -- (2.5,0);
  \draw (2.3,0) node [below] {$2538$};
  \draw (2.5,0) -- (2.5,3pt);
  \draw[time line] (2.75,2.6) -- (2.75,0);
  \draw (2.75,-0.35) node [below] {$2558$} [short line] -- +(0,0.35);
  \draw (2.75,-3pt) -- (2.75,3pt);
  \draw[time line] (4,2.6) -- (4,0);
  \draw (3.8,0) node [below] {$4058$};
  \draw (4,0) -- (4,3pt);
  \draw[time line] (4.25,1.9) -- (4.25,0);
  \draw (4.25,-0.35) node [below] {$4078$} [short line] -- +(0,0.35);
  \draw (4.25,-3pt) -- (4.25,3pt);

  \draw[time line] (5,3.3) -- (5,0);
  \draw (5,0) node [below] {$5000$};
  \draw (5,0) -- (5,3pt);
  \draw[time line] (5.5,3.3) -- (5.5,0);
  \draw (5.5,-0.35) node [below] {$5038$} [short line] -- +(0,0.35);
  \draw (5.5,-3pt) -- (5.5,3pt);
  \draw[time line] (7.5,3.3) -- (7.5,0);
  \draw (7.3,0) node [below] {$7538$};
  \draw (7.5,0) -- (7.5,3pt);
  \draw[time line] (7.75,1.9) -- (7.75,0);
  \draw (7.75,-0.35) node [below] {$7558$} [short line] -- +(0,0.35);
  \draw (7.75,-3pt) -- (7.75,3pt);

  \draw[time line] (10,3.3) -- (10,0);
  \draw (9.9,0) node [below] {$10000$};
  \draw (10,0) -- (10,3pt);
  \draw[time line] (10.5,3.3) -- (10.5,0);
  \draw (10.5,-0.35) node [below] {$10038$} [short line] -- +(0,0.35);
  \draw (10.5,-3pt) -- (10.5,3pt);
  \draw[time line] (12.5,3.3) -- (12.5,0);
  \draw (12.2,0) node [below] {$12538$};
  \draw (12.5,0) -- (12.5,3pt);
  \draw[time line] (12.75,2.6) -- (12.75,0);
  \draw (12.75,-0.35) node [below] {$12558$} [short line] -- +(0,0.35);
  \draw (12.75,-3pt) -- (12.75,3pt);
  \draw[time line] (14,2.6) -- (14,0);
  \draw (13.7,0) node [below] {$14058$};
  \draw (14,0) -- (14,3pt);
  \draw[time line] (14.25,1.9) -- (14.25,0);
  \draw (14.25,-0.35) node [below] {$14078$} [short line] -- +(0,0.35);
  \draw (14.25,-3pt) -- (14.25,3pt);
  \draw[time line] (15,1.9) -- (15,0);
  \draw (15,0) node [below] {$15000$};
  \draw (15,0) -- (15,3pt);

  % axes
  \draw[->,thick] (0,0) -- (15.7,0) node [above] {time(${\mu}s$)};
  \draw[thin] (0,0) -- (0,3.8);

  % tips of tasks
  \draw (0,0.6) node [left] {switching};
  \draw (0,1.3) node [left] {scheduling};
  \draw (0,2) node [left] {task$2$};
  \draw (0,2.7) node [left] {task$1$};
  \draw (0,3.4) node [left] {task$0$};

  % tasks
  \filldraw[system task] (0,1.2) rectangle +(0.5,0.2);
  \filldraw[periodic task] (0.5,3.3) rectangle +(2,0.2);
  \filldraw[system task] (2.5,0.5) rectangle +(0.25,0.2);
  \filldraw[periodic task] (2.75,2.6) rectangle +(1.25,0.2);
  \filldraw[system task] (4,0.5) rectangle +(0.25,0.2);
  \filldraw[periodic task] (4.25,1.9) rectangle +(0.75,0.2);

@@

  \filldraw[system task] (10,1.2) rectangle +(0.5,0.2);
  \filldraw[periodic task] (10.5,3.3) rectangle +(2,0.2);
  \filldraw[system task] (12.5,0.5) rectangle +(0.25,0.2);
  \filldraw[periodic task] (12.75,2.6) rectangle +(1.25,0.2);
  \filldraw[system task] (14,0.5) rectangle +(0.25,0.2);
  \filldraw[periodic task] (14.25,1.9) rectangle +(0.75,0.2);

  % initiation of tasks
  \foreach \x in {0,5,10}
    \draw [init] (\x,3.3) -- +(0,-0.1);
  \foreach \x in {0,10}
    \draw [init] (\x,2.6) -- +(0,-0.1);  
  \foreach \x in {0,15}
    \draw [init] (\x,1.9) -- +(0,-0.1);

  % completion of tasks
  \draw [complete] (2.5,3.5) -- +(0,0.1);
  \draw [complete] (4,2.8) -- +(0,0.1);
  \draw [complete] (7.5,3.5) -- +(0,0.1);
  \draw [complete] (12.5,3.5) -- +(0,0.1);
  \draw [complete] (14,2.8) -- +(0,0.1);

  % text
  \draw[{Stealth}-,thick] (15,2.2) -- +(0,1.5)
    node [above] {\emph{Misses Deadline!}};

  % legend
  \begin{scope}[xshift = -1.2cm]  
    \draw [fill=gray!25,draw=gray!50,dashed] (1.5,4) rectangle +(8,1);
    \draw (1.5,4.5) node [above right] {LEGEND};
    \draw [init] (2,4.4) -- +(0,-0.1);
    \draw (2.2,4.55) node [below right] {: Initiation of Tasks};
    \draw [complete] (6,4.2) -- +(0,0.1);
    \draw (6.2,4.55) node [below right] {: Completion of Tasks};
  \end{scope}

\end{tikzpicture}
\caption{An Counterexample of Scenario (iv).}
\label{f:tikz}
\end{figure*}
